### 2013-09-27 Publications/2013-ISBI14/02-introduction.tex
ISBI 2014. Almost finished!!

In-vivo whole-brain connectivity analysis has been a
research topic of high interest for the last
5 years \cite{jones_studying_2008}. 
\Gls*{dmri} can be used to probe the
orientation of fiber bundles within the brain,
generally applying \gls*{epi} sequences.
After a signal reconstruction step 
(i.e. \cite{basser_microstructural_2011}), 
tractography algorithms draw a map of the sampled 
structures.
These maps can represent the actual trajectories
of fiber bundles (deterministic tractography) or
pixel-wise probability of connection to a certain origin
(probabilistic tractography). Finally, the
information about these connections is collected
into a network matrix that can be subjected to
the so-called ``connectome analysis''.

However, such a complex workflow is prone to
flaws that have been detailedly reported 
\cite{jones_twenty-five_2010,jbabdi_tractography:_2011}.
In order to enable reliable and robust connectome
analyses of the brain, some weak processing points must
be improved. One prominent source
of inaccuracy are the susceptibility-derived artifacts,
for which \Gls*{epi} schemes are specially sensitive.
As susceptibility changes at tissue interfaces,
so does the magnetic field. The consequence of the 
inhomogeneity of the field translates in a highly 
distorted imaged anatomy and a significant signal 
destruction of certain regions of the brain 
(e.g. the orbitofrontal lobe, for the proximity of the
air surrounding sinuses). This artifact has been
profoundly described, generally within \gls*{fmri}
literature because they are usually acquired with 
\gls*{epi} as \gls*{dmri}.

>>>>

In-vivo whole-brain connectivity analysis has been a
research topic of high interest for the last
5 years. 
\Gls*{dmri} can be used to probe the
orientation of fiber bundles within the brain,
generally applying \gls*{epi} sequences.
After a signal reconstruction step, 
tractography algorithms draw a map of the sampled 
structures.
These maps can represent the actual trajectories
of fiber bundles (deterministic tractography) or
pixel-wise probability of connection to a certain origin
(probabilistic tractography). Finally, the
information about these connections is collected
into a network matrix that can be subjected to
the so-called ``connectome analysis''.

However, such a complex workflow is prone to
flaws that have been detailedly reported 
\cite{jones_twenty-five_2010}.
In order to enable reliable and robust connectome
analyses of the brain, some weak processing points must
be improved. One prominent source
of inaccuracy are the susceptibility-derived artifacts,
for which \Gls*{epi} schemes are specially sensitive.
As susceptibility changes at tissue interfaces,
so does the magnetic field. The consequence of the 
inhomogeneity of the field translates in a highly 
distorted imaged anatomy and a significant signal 
destruction of certain regions of the brain 
(e.g. the orbitofrontal lobe, for the proximity of the
air surrounding sinuses). This artifact has been
profoundly described, generally within \gls*{fmri}
literature because they are usually acquired with 
\gls*{epi} as \gls*{dmri}.
